Why there are more species in several small patches vs few large patches:

### 2023-12-04 ms_SLOSS.Rmd
Updated conclusions

In our simulations we fixed the amount of habitat loss to 60%, first it in previous simulation studies it was shown that  fragmentation was important when the habitat amount is low, around 10% [@Hanski2015; @Rybicki2013]. but it has been observed that the amount of habitat loss could influence the effect of fragmentation [@Loke2019; @With2016]. It was suggested that with very low habitat amount (e.g 7%) the arrangement of patches does not matters, this could paired with our results of stressed communities

>>>>

In previous simulation studies it was shown that  fragmentation was important when the habitat amount is low, around 10% [@Hanski2015; @Rybicki2013], but it has been observed that with levels habitat around 10-20% the effect of fragmentation is positive or have an intermediate maximum [@Loke2019; @With2016], and with lower habitat amount (e.g 7%) the arrangement of patches does not matters, we obtained similar patterns with 40% habitat amount, which is near the amount used in newer simulated studies (32%) that also obtain more species richness with more fragmentation [@Rybicki2020].

The novel aspect of our model is that it consider communities that are assembled from a metacommunity in which individuals migrate to empty habitat, and then after the number of species is stabilized the habitat is fragmented. This could be a more realistic scenario than if all species are present with initially random patterns at an already fragmented habitat [@Rybicki2020]. This could be more important the more heterogeneous was species spatial distribution pattern before fragmentation.
